Typed Interactions for NLU in Opal

### 2017-12-14 paper.tex
Changed names to Alice and Bob
Like a good CS researcher
Added a paragraph on hypothetical worlds

It turns out that this might actually be a good thing, if viewed from the
perspective of the NLU engine itself. While \ts{Absolute} and \ts{Relative} are
the same intent from a philosophical perspective, they might be parsed very
differently. The utterance
\begin{center}
  \emph{Schedule my Wednesday meeting with Chris.}
\end{center}
is very different in structure from
\begin{center}
  \emph{Set a meeting with James tomorrow.}
\end{center}
Thus, it might be the case that forcing the programmer to write slightly
different types will make it much easier for the NLU backend to find the correct
information. There is likely some work to be done in terms of making our types
more idiomatic, but for now we err on the side of making life easier for the NLU
engine.

@@

>>>>

It turns out that this might actually be a good thing, if viewed from the
perspective of the NLU engine itself. While \ts{Absolute} and \ts{Relative} are
the same intent from a philosophical perspective, they might be parsed very
differently. The utterance
\begin{center}
  \emph{Schedule my Wednesday meeting with Alice.}
\end{center}
is very different in structure from
\begin{center}
  \emph{Set a meeting with Bob tomorrow.}
\end{center}
Thus, it might be the case that forcing the programmer to write slightly
different types will make it much easier for the NLU backend to find the correct
information. There is likely some work to be done in terms of making our types
more idiomatic, but for now we err on the side of making life easier for the NLU
engine.

@@

\noindent \emph{Hypothetical Worlds}\qquad It turns out that this process of
choosing the parse with the best confidence score is a great application of one
of Opal's major features---hypothetical worlds. In a perfect world, we would
allow our parser to generate all possible response objects, compute some
function based on the confidence values for the entities in the objecs, and
choose the object with the best value of the function. Writing this code out by
hand would be tedious, inefficient, and error-prone. Hypothetical worlds give
this semantics as a language-level feature. When code is executed in a \ts{hyp}
block, its computation is entirely hypothetical. Multiple \ts{hyp} blocks can be
run in parallel, and their computations can be observed at specified points.
Once a particular world is chosen (in this case, by observing the confidence
function), a sigle world can be ``committed.'' From that point forward, only the
committed world is treated as real, and the computation can continue with the
chosen response object.

In the future, we think that hypothetical worlds will open up new opportunities
for NLU interaction, including the ability to parse responses into more complex
types.
